---
title: "Mosa Data Science"
author: "Olive"
date: "2024-01-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE,
                      message = FALSE, 
                      error = TRUE)
library(tidyverse)
library(patchwork)
library(dplyr)

dir.create("figures", showWarnings= FALSE)

```

#MOSA IG WRAPPED: June - December 2023

## Mapping the Best Performance 

```{r}

```



## Mapping the Best Time for Posting

```{r fig.height=10, fig.width=30}
mosa_timer <- ggplot(Mosa,aes(Time,Total.Reach)) + geom_point()
mosa_timer

mosa_timei <- ggplot(Mosa,aes(Time,Total.Imp)) + geom_point(color="blue")
mosa_timei
```


## Comparing Non-Followers vs. Followers to type of post

Reach is the number of people who viewed the post, divided into followers and non-followers.


```{r fig.height=10, fig.width=15}
mosa_non<-ggplot(Mosa,aes(Post.Type,Non.Followers)) + geom_boxplot(outlier.color = "red")+theme_minimal()+labs(title = "Post Type Outreach to Non-followers")+ylim(0,550)+geom_hline(yintercept=avg_non,color="blue",linetype="dashed")


mosa_fol <-ggplot(Mosa,aes(Post.Type,Followers)) + geom_boxplot(outlier.color = "red")+theme_minimal()+labs(title = "Post Type Outreach to Followers")+ ylim(0,550)+geom_hline(yintercept = avg_fol,color="blue",linetype="dashed")

mosa_non + mosa_fol

avg_non<-mean(Mosa$Non.Followers)
avg_fol<-mean(Mosa$Followers)

sd_non<-sd(Mosa$Non.Followers)
sd_fol<-sd(Mosa$Followers)

factor_reach<-avg_non/avg_fol *100

```

## Impressions

Impressions are the number of times the post was seen, and where on the app.
Home Impressions: post viewed from home feed
Profile Impressions: post viewed from Mosa profile
Hashtag Impressions: post viewed from IG hashtags

```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
